Observed vs. Simulated Year Comparison

### 2023-04-18 03-post-process/compare-sim-to-obs.Rmd
Update sim-vs-obs to use +/- 20% as okay range

  breaks = c(0, 0.25, 0.5, 0.75, 0.9, 1.1, 1.25, 1.5, 1.75, 100)
  bin_names = levels(cut(runif(1e6, 0, 2), breaks = breaks, include.lowest = TRUE))
  names(cols) = c(bin_names[1:5], bin_names[5:9])
  bins = cut(x, breaks = breaks, include.lowest = TRUE)
  cols_use = cols[as.character(bins)]
  cols_use[is.na(cols_use)] = cols[5]
  alpha(unname(cols_use), 0.5)
}

@@

  breaks = c(-1, -0.75, -0.5, -0.25, -0.1, 0.1, 0.25, 0.5, 0.75, 1)
  bin_names = levels(cut(runif(1e6, -1, 1), breaks = breaks, include.lowest = TRUE))
  names(cols) = c(bin_names[1:5], bin_names[5:9])
  bins = cut(x, breaks = breaks, include.lowest = TRUE)
  cols_use = cols[as.character(bins)]
  cols_use[is.na(cols_use)] = cols[5]
  alpha(unname(cols_use), 0.5)
}
```

@@

Values close to 1 are ideal for the mean and CV ratios and cells are color-coded based on how far they fall from 1: less than 1 are blue and greater than 1 are red; values between 0.9 and 1.1 might be considered "good enough", and have been assigned no color.

Values close to 0 are ideal for the autocorrelation differences and cells are color-coded based on how far they fall from zero: less than zero are blue and greater than zero are red; values between -0.1 and 0.1 might be considered "good enough", and have been assigned no color.

>>>>

  breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1.2, 1.4, 1.6, 1.8, 100)
  bin_names = levels(cut(runif(1e6, 0, 2), breaks = breaks, include.lowest = TRUE))
  names(cols) = c(bin_names[1:5], bin_names[5:9])
  bins = cut(x, breaks = breaks, include.lowest = TRUE)
  cols_use = cols[as.character(bins)]
  cols_use[is.na(cols_use)] = cols[5]
  alpha(unname(cols_use), 0.5)
}

@@

  breaks = c(-1, -0.8, -0.6, -0.4, -0.2, 0.2, 0.4, 0.6, 0.8, 1)
  bin_names = levels(cut(runif(1e6, -1, 1), breaks = breaks, include.lowest = TRUE))
  names(cols) = c(bin_names[1:5], bin_names[5:9])
  bins = cut(x, breaks = breaks, include.lowest = TRUE)
  cols_use = cols[as.character(bins)]
  cols_use[is.na(cols_use)] = cols[5]
  alpha(unname(cols_use), 0.5)
}
```

@@

Values close to 1 are ideal for the mean and CV ratios and cells are color-coded based on how far they fall from 1: less than 1 are blue and greater than 1 are red; values between 0.8 and 1.2 (i.e., <20% off) might be considered "good enough", and have been assigned no color.

Values close to 0 are ideal for the autocorrelation differences and cells are color-coded based on how far they fall from zero: less than zero are blue and greater than zero are red; values between -0.2 and 0.2 might be considered "good enough", and have been assigned no color.
